%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass{sig-alternate}

\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{url}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage{verbatim}

%\newcommand{\keywords}[1]{\par\addvspace\baselineskip
%\noindent\keywordname\enspace\ignorespaces#1}

% todo macro
\usepackage{color}
\newtheorem{deflda}{Axiom}
\newcommand{\todo}[1]{\noindent\textcolor{red}{{\bf \{TODO}: #1{\bf \}}}}
\newcommand{\neon}{NeOn }
\newcommand{\protege}{Prot{\'e}g{\'e} }



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Beginning of document  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% first the title is needed
% --- ACM copyright metadata here ---
%\conferenceinfo{SEM}{14, September 04 - 05 2014, Leipzig, AA, Germany}
%\CopyrightYear{2015}
%\crdata{978-1-4503-2927-9/14/09.}


%\title{How to access and reuse ontologies in real-world scenarios}
\title{Promoting Reuse within Ontology Engineering in a Linked Data World}

\numberofauthors{3}
\author{
% 1st. author
\alignauthor Ghislain Auguste Atemezing\\
       \affaddr{MONDECA}\\
       \affaddr{35 boulevard Strasbourg, Paris, France}\\
       \email{\small{ghislain.atemezing@mondeca.com}}
% 3rd author
  \alignauthor Nuria Garc{\'i}a-Santa\\
       \affaddr{Expert System Iberia}\\
       \affaddr{Campo de las Naciones, Madrid, Spain.}\\
       \email{\small{ngarcia@expertsystem.com}}
% 2nd. author
\alignauthor Boris Villaz{\'o}n-Terrazas\\
       \affaddr{Expert System Iberia}\\
       \affaddr{Campo de las Naciones, Madrid, Spain.}\\
       \email{\small{bvillazon@expertsystem.com}}       
}

\maketitle


%%%%%%%%%%%%%%%%%%
%%%  Abstract  %%%
%%%%%%%%%%%%%%%%%%

\begin{abstract}
Developing ontologies by reusing already available and well-known ontologies, is commonly acknowledged to play a crucial role to facilitate inclusion and expansion of the Web of Data. Some recommendations exist to guide ontology engineers, but those recommendations do not provide guidelines on how to reuse fine-grained vocabulary elements, i.e., reusing specific classes and properties. Moreover, it is still hard to find a tool that promotes and facilitates the reuse of available terms when building ontologies. This paper presents (1) a set of guidelines for reusing fine-grained vocabulary elements, and (2) a technological support for such guidelines, Prot{\'e}g{\'e}LOV. Prot{\'e}g{\'e}LOV is a plugin for the ontology editor which combines the access to the Linked Open Vocabularies (LOV) during ontology modelling. It allows users to search a term in LOV and provides actions to include the external term in the ontology being developed. Results from a preliminary user study indicate that the proposed guidelines using Prot{\'e}g{\'e}LOV can booster the access and reuse of terms of existing vocabularies.
%\keywords{ontology engineering, ontology reuse, LOV, Prot{\'e}g{\'e}, Plugin} 
\end{abstract}

% Categories for the papers.
%\todo{Replace with the categories provided by Nuria}
%\category{M}{Knowledge Management}
%\category{M.1}{Knowledge engineering methodologies}
%\category{M.1}{Knowledge engineering methodologies}
%\category{M.8.}{Knowledge Reuse}
\category{H.4}{Information Systems Applications}{Miscellaneous}
\category{H.3.5}{Online Information Services}{Data sharing}[Web-based services]

\terms{Accessibility, Linked Data, Vocabularies}

\keywords{Ontology engineering, Ontology reuse, LOV, Prot{\'e}g{\'e}, Plugin}



%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  1. Introduction  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{3mm}
\section{Introduction}\label{sec:introduction}
\input{intro}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  2. Related work  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{10mm}.
\section{Related Work}\label{sec:soa}
\input{relatedwork}


\vspace{3mm}.
\section{Reusing vocabulary terms\\ when building ontologies}\label{sec:reuse}
\input{method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  3.LOV APIs Description  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{-3mm}
%\section{Linked Open Vocabulaires (LOV)}\label{sec:lov}
\vspace{3mm}.
\section{Technological Support}
%\vspace{-3mm}
\input{lov}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  4.ProtegeLOV Description  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\vspace{-3mm}
%\section{Prot{\'e}g{\'e}LOV}\label{sec:classification}
%\input{plugin-core}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  5. Conclusion and Future Work  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{3mm}
\section{Evaluation}\label{sec:conclusion}
\input{conclusions}



%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Acknowledgments  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{1mm}
\paragraph{\textbf{Acknowledgments.}} %\label{sec:acknowledgments}
Thanks to Pierre-Yves and the LOV team for maintaining the LOV catalog and the API access. This work has been supported by the KDrive Project.
% More acknowledgments here
%\vspace{-3mm}

\bibliographystyle{abbrv}
%\nocite{*}
\bibliography{isemanticsbib}
\balancecolumns
\end{document}
