%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%   %%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage[utf8]{inputenc}
\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{url}
\usepackage{listings}
\usepackage{subfigure}
\usepackage{algorithmic}
\usepackage{algorithm}

\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

% todo macro
\usepackage{color}
\newtheorem{deflda}{Axiom}
\newcommand{\todo}[1]{\noindent\textcolor{red}{{\bf \{TODO}: #1{\bf \}}}}
\newcommand{\neon}{NeOn }
\newcommand{\protege}{Prot{\'e}g{\'e} }

% Language Definitions for Turtle
\definecolor{olivegreen}{rgb}{0.2,0.8,0.5}
\definecolor{grey}{rgb}{0.5,0.5,0.5}
\lstdefinelanguage{ttl}{
sensitive=true,
morecomment=[l][\color{brown}]{@},
morecomment=[l][\color{red}]{\#},
morestring=[b][\color{blue}]\",
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Beginning of document  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% first the title is needed

\title{The Prot{\'e}g{\'e}LOV Plugin: Ontology Access and Reuse for Everyone }


\author{ Nuria Garc\'ia-Santa\inst{1}, Ghislain Auguste Atemezing\inst{2},\\ and Boris Villaz{\'o}n-Terrazas\inst{1}}

\institute{
Expert System Iberia, Campo de las Naciones, Madrid, Spain. \\
\and MONDECA, 35 boulevard de Strasbourg, Paris, France .\\
\email{ngarcia@expertsystem.com,ghislain.atemezing@mondeca.com,bvillazon@expertsystem.com \\
}
}  

\authorrunning{Nuria Garc\'ia-Santa, G.A. Atemezing, B. Villaz{\'o}n-Terrazas}
\maketitle

%%%%%%%%%%%%%%%%%%
%%%  Abstract  %%%
%%%%%%%%%%%%%%%%%%

\begin{abstract}
Developing ontologies, by reusing already available and well-known ontologies, is commonly acknowledge to play a crucial role to facilitate inclusion and expansion of the Web of Data. Some recommendations exist to guide ontologists in ontology engineering, but they do not provide guidelines on how to reuse vocabularies at low fine grained, i.e., reusing specific classes and properties. Moreover, there is still hard to find a tool that provides users with an environment to reuse terms. This paper presents Prot{\'e}g{\'e}LOV, a plugin for the ontology editor Prot{\'e}g{\'e}, that combines the access to the Linked Open Vocabularies (LOV) during ontology modeling. It allows users to search a term in LOV and provides three actions if the term exists : (i) replace the selected term in the current ontology; (ii) add the {\tt rdfs:subClassOf} or {\tt rdfs:subPropretyOf} axiom between the selected term and the local term; and (iii) add the {\tt owl:equivalentClass} or {\tt owl:equivalentProperty} between the selected term and local term. Results from a preliminary user study indicate that Prot{\'e}g{\'e}LOV does provide an intuitive access and reuse of terms in external vocabularies.
\keywords{ontology engineering, ontology reuse, LOV, Prot{\'e}g{\'e}, Plugin} 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  1. Introduction  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{-3mm}
\section{Introduction}\label{sec:introduction}
\input{intro}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  2. Related work  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\section{Related Work}\label{sec:soa}
\vspace{-3mm}
\input{relatedwork}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  3.LOV APIs Description  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\section{Linked Open Vocabulaires (LOV)}\label{sec:lov}
\vspace{-3mm}
\input{lov}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  4.ProtegeLOV Description  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\section{Prot{\'e}g{\'e}LOV}\label{sec:classification}
\input{plugin-core}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  5. Conclusion and Future Work  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-3mm}
\section{Evaluation}\label{sec:conclusion}
\input{conclusions}



%%%%%%%%%%%%%%%%%%%%%%%%%
%%%  Acknowledgments  %%%
%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{-1mm}
\paragraph{\textbf{Acknowledgments.}} %\label{sec:acknowledgments}
Thanks to Pierre-Yves and the LOV team for providing and maintaining a curated vocabularies and API access.
% More acknowledgments here
\vspace{-3mm}
\bibliographystyle{abbrv}
%\nocite{*}
\bibliography{eswcbib}
\end{document}
